My title

### 2024-11-04 paper/paper.qmd
Added figures to data section

library(tidyverse)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)
library(knitr)
library(webshot2)

@@

Add graphs, tables and text.
Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = "none") +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
```

Talk more about it.

And also planes (@fig-planes).
(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

# analysis_data |> 
#   ggplot(aes(x = width, y = length)) +
#   geom_point(alpha = 0.8) +
#   theme_minimal() +
#   labs(x = "Wing width (mm)",
#        y = "Wing length (mm)")
```

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: SummaryStatisticsComparison
#| tbl-cap: Directly compares support percentages and sample sizes for Harris and Trump, showing central tendencies and variability in polling data for each candidate.

@@

# Appendix {-}

>>>>

library(tidyverse)
library(testthat)
library(arrow)
library(here)
library(rstanarm)
library(bayesplot)
library(gt)
library(kableExtra)

@@

The primary outcome variable in our analysis is the percentage of support each candidate receives in various polls, as reported by different polling organizations.
This variable captures the proportion of respondents who indicate support for a specific candidate (e.g., Kamala Harris, Donald Trump) in a given poll.
By aggregating the reported percentages across pollsters and accounting for factors such as sample size and pollster reliability, we can obtain a comprehensive view of each candidate's current standing in the 2024 U.S. election.
This outcome variable directly reflects voter preference trends and provides a baseline for modeling anticipated election results.
The robustness of this measure is influenced by the accuracy of individual poll data and the methodological rigor of each pollster, such as Emerson’s use of IVR and online panels, ensuring it represents a reliable indicator of the broader electorate's sentiments.

To illustrate the predicted support for the two primary candidates in our analysis, Kamala Harris and Donald Trump, we included a density plot @fig-avg-support that visualizes the simulated support percentages for each candidate.
This plot provides a comparison of predicted support, with Harris shown in blue and Trump in red.
The density plot highlights the distribution of predicted support percentages based on our model simulations, allowing us to observe both the central tendency and spread of each candidate’s support.

In this visual, we can see that Harris and Trump exhibit overlapping distributions, though with slightly different peaks.
This overlapping region reflects a competitive election landscape, where variations in poll results or sampling could impact the projected outcome.
The density peaks suggest that Harris has a slightly higher central tendency in predicted support, yet the close proximity of both distributions emphasizes the uncertainty and competitiveness of the race.
By examining the density of predicted percentages, this plot contributes to a clearer understanding of the variability in support for each candidate as forecasted by our model.

```{r}
#| label: fig-avg-support
#| fig-cap: This density plot compares the predicted support percentages for Kamala Harris and Donald Trump based on model simulations."
#| echo: false
#| warning: false
#| message: false

harris_model <- readRDS(here("models/harris_model.rds"))
trump_model <- readRDS(here("models/trump_model.rds"))

harris_pred <- posterior_predict(harris_model)
harris_pred_means <- colMeans(harris_pred)
trump_pred <- posterior_predict(trump_model)
trump_pred_means <- colMeans(trump_pred)

# Simulate election outcomes by comparing Harris and Trump's predicted support
simulated_outcomes <- ifelse(harris_pred_means > trump_pred_means, "Harris", "Trump")

# Determine the minimum length between the two prediction sets
min_length <- min(length(harris_pred_means), length(trump_pred_means))

# Subset both predictions to have the same length
harris_pred_means <- harris_pred_means[1:min_length]
trump_pred_means <- trump_pred_means[1:min_length]

# Combine predictions for comparison plot
comparison_data <- data.frame(
  support = c(harris_pred_means, trump_pred_means),
  candidate = rep(c("Harris", "Trump"), each = min_length)
)

# Plot comparison of support for Harris and Trump
ggplot(comparison_data, aes(x = support, fill = candidate)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Comparison of Predicted Support for \n     Harris and Trump",
    x = "Predicted Support Percentage",
    y = "Density",
    fill = "Candidate",
  ) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_minimal(base_size = 14)
```

@@

To model the outcome variable effectively, we selected 3 predictor variables based on their relevance to candidate support and regional trends:

Pollster Name: Identifying the organization conducting each poll (e.g., YouGov, Emerson) allows us to assess potential biases and variation in methodologies that could impact polling accuracy.
Given that certain pollsters (like Emerson) have more frequent entries in our cleaned dataset, this predictor provides valuable insight into consistency and reliability across poll sources.

Sample Size: Poll sample size directly influences the reliability of the reported percentages.
Polls with larger sample sizes tend to yield more accurate estimates, reducing margin of error and providing a more representative snapshot of voter opinion.
Incorporating this variable enhances the robustness of our predictions by weighting polls based on their sample adequacy.

State: Including the state where each poll was conducted allows us to account for regional voting patterns, which are essential in a federal system like the U.S.
Electoral College.
State-level data provides insights into geographic trends and helps us model potential outcomes across electoral regions.

Each predictor variable was selected to provide a balanced perspective on polling results, helping us account for various factors that influence voter behavior and polling reliability.
These variables offer a structured approach to analyzing the 2024 U.S. election, supporting a model that is both statistically grounded and contextually aware.

@fig-pollster-vs-reliability illustrates the distribution of numeric reliability grades for the five most frequent pollsters in the dataset: Beacon/Shaw, Emerson, Morning Consult, Redfield & Wilton Strategies, and Siena/NYT. Each boxplot represents the variation in numeric reliability grades for individual polls from these pollsters, with jittered points indicating individual poll grades. This visualization helps highlight the consistency of reliability scores across these pollsters, with Emerson and Morning Consult exhibiting particularly stable distributions around higher reliability grades compared to others.

This reliability assessment is crucial in weighting pollster data appropriately in our analysis. For example, Emerson, one of the most frequent pollsters in the dataset, shows a narrow spread in its reliability score, suggesting consistent methodology and accuracy. By understanding the reliability of each pollster, we can adjust our model to account for potential biases or methodological weaknesses that might otherwise skew the results. This reliability variable acts as a quality measure, allowing us to place greater confidence in polls from consistently high-rated pollsters.

```{r}
#| label: fig-pollster-vs-reliability
#| fig-cap: Each boxplot shows the distribution of numeric reliability grades for the top 5 pollsters, with individual poll grades represented by jittered points.
#| echo: false
#| warning: false
#| message: false

# Pollster reliability visualization
# Identifying the 5 most frequent pollsters for readability 
top_pollsters <- analysis_data %>%
  count(pollster_name, sort = TRUE) %>%
  top_n(5, n) %>%
  pull(pollster_name)

# Filter data to include only the top 5 pollsters
top_pollsters_data <- analysis_data %>%
  filter(pollster_name %in% top_pollsters)

# Visualize numeric grade fort he 5 top pollsters
ggplot(top_pollsters_data, aes(x = pollster_name, y = numeric_grade)) +
  geom_boxplot(aes(fill = pollster_name), color = "black", width = 0.6, outlier.shape = NA, alpha = 0.8) +
  geom_jitter(color = "skyblue", size = 1, alpha = 0.6, width = 0.2) +  # Add jittered points for individual grades
  labs(
    title = "Reliability Score of Top 5 Pollsters \nby Frequency",
    subtitle = "Numeric Grade Distribution of Most Frequent Pollsters",
    x = "Pollster Name",
    y = "Numeric Grade",
  ) +
  scale_fill_brewer(palette = "Set3") +  # Use a visually appealing color palette
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 14, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(angle = 30, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
    plot.margin = margin(t = 15, r = 15, b = 15, l = 15))
```

@fig-state-vs-size provides a breakdown of sample sizes across different U.S. states, with Pennsylvania, Michigan, and Wisconsin leading in terms of sample volume. These sample sizes are a critical predictor, as polls with larger sample sizes generally yield more reliable data. This visualization underscores the emphasis placed on certain swing states and battleground regions, reflecting where polling efforts are most concentrated and, by extension, where voter sentiment may be considered more closely in analyses.

Incorporating sample size as a predictor allows the model to adjust the weight of each poll based on its reliability. For instance, a poll with a large sample size from a critical state such as Pennsylvania is likely to be more indicative of statewide voter sentiment than a poll with a smaller sample size. This adjustment based on sample size helps to create a more nuanced and representative model, giving us a stronger basis for forecasting outcomes in the election.

```{r}
#| label: fig-state-vs-size
#| fig-cap: This chart displays the total sample size per state for survey data, ordered from highest to lowest sample size.
#| echo: false
#| warning: false
#| message: false

# Prepare the data by grouping and summarizing sample size per state
state_sample_data <- analysis_data %>%
  group_by(state) %>%
  summarize(total_sample_size = sum(sample_size, na.rm = TRUE)) %>%
  arrange(desc(total_sample_size))  # Order by sample size for better readability

# Horizontal bar plot for sample size by state
# Horizontal bar plot for sample size by state
ggplot(state_sample_data, aes(x = reorder(state, total_sample_size), y = total_sample_size)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black", alpha = 0.7) +
  coord_flip() +  # Flip coordinates for a horizontal bar plot
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Total Sample Size by State",
    x = "State",
    y = "Sample Size",
    caption = "Fig 3: This chart displays the total sample size per state for survey data, ordered from highest to lowest sample size."
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 7, hjust = 1),  # Adjust size for readability
    axis.text.x = element_text(size = 12),
    plot.caption = element_text(size = 8, hjust = 0, margin = margin(t = 10))
  )

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: SummaryStatisticsComparison
#| tbl-cap: Directly compares support percentages and sample sizes for Harris and Trump, showing central tendencies and variability in polling data for each candidate.

@@

# Appendix {.unnumbered}
